Figure 6 - networks

### 2024-08-04 ms_figure_6_networks.Rmd
Some clarifications in Fig6

---
title: "Figure 6 - networks"
author: "Charlotte Soneson, Michael Stadler, Merle Skribbe"
date: "`r Sys.Date()`"
output: 
    html_document:
        theme: united
        toc: true
        toc_float: true
        code_folding: hide
params:
    rds150: "data/ipms_150_sce.rds"
    coords150: "data/visnetwork_coords_150.csv"
    rds500: "data/ipms_500_sce.rds"
    coords500: "data/visnetwork_coords_500.csv"
    rds150untag: "data/ipms_150_untag_sce.rds"
    interactors: "data/Gene_list_TFinteractors_Pombase20240226.txt"
    idmap: "data/id_mapping_table.txt"
    rad24_rad25_tbl: "data/FigS5_Rad24_Rad25_interactingTFs_list_motifs.txt"
editor_options: 
    chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dev = c("png", "cairo_pdf"))
```

@@

```{r get-similarities, class.source="fold-show"}
simil150 <- simsFromResults(sce150)
simil500 <- simsFromResults(sce500)
maxSimil <- round(max(max(simil150$simil, na.rm = TRUE),
                      max(simil500$simil, na.rm = TRUE)), 1)
```

@@

        ## Format positions
        nodes_positions <- reactive({
            positions <- input$visnetwork_positions
            if (!is.null(positions)){
                nodes_positions <- do.call("rbind", lapply(positions, function(x){data.frame(x = x$x, y = x$y)}))
                nodes_positions$id <- names(positions)
                nodes_positions
            } else {
                NULL
            }
        })

@@

## Create small example similarity matrix and graph, for three selected proteins
poi <- c("Atf1", "Pcr1", "Arp8")
simil150example <- simsFromResults(sce150[poi, ])
gr150example <- createNetwork(similList = simil150example, threshold = 4.5,
                              known_interactors = interactors, 
                              settings = "igraph")

@@

## Put together
fig5a <- cowplot::plot_grid(
    cowplot::plot_grid(
        tplot, 
        get_legend(ggeqn1, "right"), 
        similplot + theme(legend.position = "bottom"), 
        ggr150example + theme(legend.position = "none"), 
        align = "v", axis = "t", 
        labels = c("A", "", "", ""), nrow = 1, 
        rel_widths = c(1.1, 0.9, 1, 0.5)
    ),
    ggeqn2, ncol = 1, labels = "", 
    rel_heights = c(3, 1)
)
```

@@

plot_grid(
    fig5a, 
    plot_grid(hm_rad, ggtbl, nrow = 1, align = "h", axis = "b", 
              rel_widths = c(2, 2.5), labels = c("B", "C")),
    rel_heights = c(1, 3), ncol = 1,
    labels = c("A", "")
)
```

>>>>

---
title: "Figure 6 - networks"
author: "Charlotte Soneson, Michael Stadler, Merle Skribbe"
date: "`r Sys.Date()`"
output: 
    html_document:
        theme: united
        toc: true
        toc_float: true
        code_folding: hide
params:
    rds150: "data/ipms_150_sce.rds"
    coords150: "data/visnetwork_coords_150.csv"
    rds500: "data/ipms_500_sce.rds"
    coords500: "data/visnetwork_coords_500.csv"
    rds150untag: "data/ipms_150_untag_sce.rds"
    interactors: "data/Gene_list_TFinteractors_Pombase20240226.txt"
    idmap: "data/id_mapping_table.txt"
    rad24_rad25_tbl: "data/FigS6_Rad24_Rad25_interactingTFs_list_motifs.txt"
editor_options: 
    chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dev = c("png", "cairo_pdf"))
options(scipen = 6)
```

@@

```{r get-similarities, class.source="fold-show"}
simil150 <- simsFromResults(sce150, adjpThr = 0.1)
simil500 <- simsFromResults(sce500, adjpThr = 0.1)
maxSimil <- round(max(max(simil150$simil, na.rm = TRUE),
                      max(simil500$simil, na.rm = TRUE)), 1)
```

@@

        ## Format positions
        nodes_positions <- reactive({
            positions <- input$visnetwork_positions
            if (!is.null(positions)) {
                nodes_positions <- do.call("rbind", lapply(positions, function(x){data.frame(x = x$x, y = x$y)}))
                nodes_positions$id <- names(positions)
                nodes_positions
            } else {
                NULL
            }
        })

@@

## Create small example similarity matrix and graph, for three selected proteins
poi <- c("Atf1", "Pcr1", "Arp8")
simil150example <- simsFromResults(sce150[poi, ])
gr150example <- createNetwork(similList = simil150example, threshold = 6,
                              known_interactors = interactors, 
                              settings = "igraph")

@@

## Put together
figs6a <- cowplot::plot_grid(
    cowplot::plot_grid(
        tplot, 
        get_legend(ggeqn1, "right"), 
        similplot + theme(legend.position = "bottom"), 
        ggr150example + theme(legend.position = "none"), 
        align = "v", axis = "t", 
        labels = c("A", "", "", ""), nrow = 1, 
        rel_widths = c(1.1, 0.9, 1, 0.5)
    ),
    ggeqn2, ncol = 1, labels = "", 
    rel_heights = c(3, 1)
)
```

@@

plot_grid(
    figs6a, 
    plot_grid(hm_rad, ggtbl, nrow = 1, align = "h", axis = "b", 
              rel_widths = c(2, 2.5), labels = c("B", "C")),
    rel_heights = c(1, 3), ncol = 1,
    labels = c("A", "")
)
```
